Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-09-09 ms_pre_post.Rmd
Add third section of the Results

Figure 3 will show constraints on $M_{p}$ affecting $F_{p}$, while Figure 2 will be used again to show constraints on $F_{p}$ affecting $M_{p}$.

>>>>

Figure 3 shows evolution of tendency for polyandry and inbreeding fertilisation strategy when inbreeding mating strategy is fixed so that females must mate randomly (blue line at $M_{a}=0$). For all cost combinations of tendency for polyandry and inbreeding fertilisation strategy (Figure 3 panels A-D), we observed selection for positive values of tendency for polyandry alleles and negative values of inbreeding fertilisation strategy alleles, which we interpret as strong evidence for evolution of polyandry and associated inbreeding avoidance through fertiisation bias. This pattern of evolution contrasts with that observed when inbreeding mating strategy was not fixed, indicating that constraints on evolution of inbreeding mating strategy increased the strength for evolution of polyandry and inbreeding avoidance through fertilisation bias. For example, in Figures 1C,D,G,H, tendency for polyandry allele values are typically less than zero, reflecting evolution of monandry, and inbreeding fertilisation strategy allele values were not as negative as they were in simulations with fixed random mating (Figure 3). In general, when females were unable to avoid mating with relatives given severe inbreeding depression ($\beta=3$), selection for evolution of polyandry and post-copulatory inbreeding avoidance was strengthened.

Figure 2, which we previously contrasted with Figure 1 to test whether or not evolution of inbreeding fertilisation strategy faciitates selection for polyandry, shows evolution of tendency for polyandry and inbreeding mating strategy when inbreeding fertilisation strategy is fixed such that the sire of a focal female's offspring is randomly assigned from her mates according to a fair raffle. In all cost combinations of Figure 2 (panels A-D), tendency for polyandry allele values decreased over generations, reflecting evolution of monandry. However, values of inbreeding mating strategy alleles did not greatly differ over generations when inbreeding fertilisation strategy was fixed, meaning that the effect of fixed inbreeding fertilisation strategy on increasing selection for inbreeding avoidance through mate choice was weak or nelgigible. A weak effect is discernable in the contrast between Figure 2B and Figure 1B, in which the grand mean inbreeding mating strategy allele value is $-0.627$ when inbreeding fertilisation strategy is not fixed (Figure 1B) versus $-1.036$ when it is fixed (Figure 2B) in generation 10000. Therefore, when females were unable to bias fertilisatin to avoid inbreeding given severe inbreeding depression ($\beta=3$), selection for evolution of pre-copulatory inbreeding avoidance was not greatly strengthened.

<!--- Figure 3 will show constraints on $M_{p}$ affecting $F_{p}$, while Figure 2 will be used again to show constraints on $F_{p}$ affecting $M_{p}$. --->
